\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-18 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Section IV

\begin{figure}[t]
\centering
\includegraphics[width=.8\linewidth]{BlockDiagm.pdf}
\caption{\small{Schematic of the proposed proximal algorithm for propagating the joint state PDF as probability weighted scattered point cloud $\{\bm{x}_{k}^{i},\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$. The states $\{\bm{x}_{k}^{i}\}_{i=1}^{N}$ are updated by the Euler-Maruyama scheme applied to (\ref{ItoSDEvectorlevel}); the corresponding probability weights $\{\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ are updated via discrete version of the proximal recursion (\ref{KineticProx}).}}
\label{fig:BlockDiagm}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=.8\linewidth]{BlockDiagm.pdf}
\caption{\small{Schematic of the proposed proximal algorithm for propagating the joint state PDF as probability weighted scattered point cloud $\{\bm{x}_{k}^{i},\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$. The states $\{\bm{x}_{k}^{i}\}_{i=1}^{N}$ are updated by the Euler-Maruyama scheme applied to (\ref{ItoSDEvectorlevel}); the corresponding probability weights $\{\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ are updated via discrete version of the proximal recursion (\ref{KineticProx}) as detailed in Sec. \ref{sec:ProxAlgo}.}}
\label{fig:BlockDiagm}
\end{figure}
